\( \tool \): JavaScript IR-based Semantics Extraction Toolchain

### 2020-03-26 ase20/main.tex
Applied ASE 2020 format
[ASE] revised abstract

\documentclass[sigconf,review,anonymous=true]{acmart}

\usepackage{kotex}
\usepackage[T1]{fontenc}
\usepackage{beramono}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{qtree}
\usepackage{multirow}
\usepackage{colortbl}
\usepackage{ulem}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{listings}
\usepackage{enumitem}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{booktabs}

@@

\author{Jihyeok Park}
\email{jhpark0223@kaist.ac.kr}
\affiliation{\institution{KAIST}}

\author{Jihee Park}
\email{j31d0@kaist.ac.kr}
\affiliation{\institution{KAIST}}

\author{Sukyoung Ryu}
\email{sryu.cs@kaist.ac.kr}
\affiliation{\institution{KAIST}}

\begin{abstract}
JavaScript was initially designed for client-side code in web browsers,
but its engine is now embedded in various kinds of host software.
Despite its popularity, since the JavaScript semantics is complex
especially due to its dynamic nature, understanding and reasoning
about JavaScript programs are challenging tasks.  Thus,
researchers have proposed several attempts to define the formal semantics
of JavaScript based on ECMAScript, the official JavaScript specification.
However, the existing approaches are manual, labor-intensive, and
error-prone, and they all target only the ECMAScript 5.1 version.
This problem is critical in understanding recent JavaScript programs
because ECMAScript has been annually released since 2015, which made
already five updates after ECMAScript 5.1.

To alleviate the problem, we propose \( \tool \), a JavaScript IR-based Semantics
Extraction Toolchain. It \textit{synthesizes} a JavaScript
parser for a given grammar written in \( \bnfes \), an extended BNF
used in ECMAScript. It also \textit{automatically} extracts
semantics using rule-based compilation. Each \textit{compile rule}
describes how to convert each abstract algorithm written in a structured natural language
into functions written in \( \ires \), an Intermediate Representation
for ECMAScript. \( \tool \) synthesizes parsers from all \( \bnfes \) productions
and extracts semantics from 91.60\% of algorithm steps for five recent
ECMAScript versions.  We implemented a JavaScript interpreter for ECMAScript 2020
using the extracted semantics.  It passed 19,220 of 19,282 applicable tests
in Test262, the official ECMAScript conformance test suite. While extracting
the semantics using \( \tool \), we found three specification errors
and all of them were confirmed by TC 39. Moreover, we also successfully applied
our tool to an incomplete proposal as a case study.
\end{abstract}

\keywords{
  JavaScript,
  mechanized formal semantics,
  program synthesis
}

\maketitle

>>>>

\documentclass[sigconf,review,anonymous]{acmart}

\usepackage{url}
\usepackage{amsmath, amssymb}
\usepackage{natbib}
\usepackage{kotex}
\usepackage[T1]{fontenc}
\usepackage{beramono}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{qtree}
\usepackage{multirow}
\usepackage{colortbl}
\usepackage{ulem}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{listings}
\usepackage{enumitem}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{booktabs}

% remove ACM Reference format
\settopmatter{printacmref=false}

@@

\author{Jihyeok Park}
\affiliation{%
  \institution{KAIST}
  \department{School of Computing}
  \city{Daejeon}
  \country{South Korea}
}
\email{jhpark0223@kaist.ac.kr}

\author{Jihee Park}
\affiliation{%
  \institution{KAIST}
  \department{School of Computing}
  \city{Daejeon}
  \country{South Korea}
}
\email{j31d0@kaist.ac.kr}

\author{Sukyoung Ryu}
\affiliation{%
  \institution{KAIST}
  \department{School of Computing}
  \city{Daejeon}
  \country{South Korea}
}
\email{sryu.cs@kaist.ac.kr}

\input{abstract}
\keywords{JavaScript, mechanized formal semantics, program synthesis}
\maketitle
